rethinking and the 5 genera

### 2021-07-13 scripts/54_rethinking_binary.Rmd
udpate

# the std of b is 2, since we assume the microbiome could have big impact on immunology (based on our previous understanding and knowledge )
precis(mtox,  prob = 0.95)
plot(precis(mtox, depth = 2, prob = 0.95 ) , pars = ('b'), labels = c('simpson_reciprocal'))
# there is baseline difference between penn and Msk and MSK has higher tox rage in general.
# it doesn't seem diversity has a clear association with tox rate after correcting for center wise difference
div_value <- c(-1, 1)

@@

>>>>

# the std of b is 2, since we assume the microbiome could have big impact on immunology (based on our previous understanding and knowledge )
precis(mtox,  prob = 0.95)
plot(precis(mtox, depth = 2, prob = 0.95 ) , pars = ('b'), labels = c('simpson_reciprocal'))

# make this plot myself with a pre-defined range in the axis
df <- precis(mtox,  prob = 0.95)  %>% as.tibble()
df <- df %>%
  mutate(variable = 'simpson_reciprocal')

#remove row number 1 (The intercept)
df %>% 
  ggplot(aes(x = reorder(variable, mean), y = mean)) +
  geom_point(shape = 15,
             size  = 4, width = 0.1,
             position = "dodge", color="black") +
  geom_errorbar(aes(ymin  = `2.5%`,
                    ymax  = `97.5%`),
                width = 0.1,
                size  = 0.7,
                position = "dodge", color="turquoise4") +
  theme(axis.title = element_text(face = "bold")) +
  xlab("Variables") + ylab("Coefficient with 95% CI") +
  coord_flip(ylim = c(-0.7, 1)) +
  #geom_hline(yintercept = 1, color = "red", size = 1) +
   theme(axis.title = element_text(size = 0)) +
  theme(axis.text = element_text(size = 14)) +
  labs(title = 'Toxicity') +
  ggsave('../figs/amplicon/bayesian_div_tox.pdf', width = 5, height = 4)

```{r}
# there is baseline difference between penn and Msk and MSK has higher tox rage in general.
# it doesn't seem diversity has a clear association with tox rate after correcting for center wise difference
div_value <- c(-1, 1)

@@

```{r}
# make this plot myself with a pre-defined range in the axis
df <- precis(mcr,  prob = 0.95)  %>% as.tibble()
df <- df %>%
  mutate(variable = 'simpson_reciprocal')

#remove row number 1 (The intercept)
df %>% 
  ggplot(aes(x = reorder(variable, mean), y = mean)) +
  geom_point(shape = 15,
             size  = 4, width = 0.1,
             position = "dodge", color="black") +
  geom_errorbar(aes(ymin  = `2.5%`,
                    ymax  = `97.5%`),
                width = 0.1,
                size  = 0.7,
                position = "dodge", color="turquoise4") +
  theme(axis.title = element_text(face = "bold")) +
  xlab("Variables") + ylab("Coefficient with 95% CI") +
  coord_flip(ylim = c(-0.7, 1)) +
  #geom_hline(yintercept = 1, color = "red", size = 1) +
   theme(axis.title = element_text(size = 0)) +
  theme(axis.text = element_text(size = 14)) +
  labs(title = 'CR') +
  ggsave('../figs/amplicon/bayesian_div_cr.pdf', width = 5, height = 4)
```

### 2021-07-13 scripts/56_rethinking_genera.Rmd
back from my wonderful vacation
udpate

```{r}
library(rethinking)
library(tidyverse)  
library(ggpubr)
```

@@

```{r}
gtox <- ulam(
    alist(
        tox ~ dbinom( 1 , p ) ,
        logit(p) <- ba*Akkermansia + bb*Bacteroides + be*Enterococcus + bf*Faecalibacterium + br*Ruminococcus + a[location] ,
        ba ~ dnorm( 0 , 1),
        bb ~ dnorm( 0 , 1),
        be ~ dnorm( 0 , 1),
        bf ~ dnorm( 0 , 1),
        br ~ dnorm( 0 , 1),
        a[location] ~ dnorm( 0 , 0.5 )
    ) , data=dat_list , chains=4 , log_lik=TRUE , cores = 8)
precis(gtox, prob = 0.95)   
plot(precis(gtox, depth = 2, prob = 0.95) )  
# indicative of the Bacteroides link with toxicity  
```

@@

>>>>

```{r}
library(rethinking)
library(tidyverse)  
library(ggpubr)
set.seed(123)
```

@@

```{r}
gtox <- ulam(
    alist(
        tox ~ dbinom( 1 , p ) ,
        logit(p) <- ba*Akkermansia + bb*Bacteroides + be*Enterococcus + bf*Faecalibacterium + br*Ruminococcus + a[location] ,
        ba ~ dnorm( 0 , 1),
        bb ~ dnorm( 0 , 1),
        be ~ dnorm( 0 , 1),
        bf ~ dnorm( 0 , 1),
        br ~ dnorm( 0 , 1),
        a[location] ~ dnorm( 0 , 0.5 )
    ) , data=dat_list , chains=4 , log_lik=TRUE , cores = 16)
precis(gtox, prob = 0.95)   
plot(precis(gtox, depth = 2, prob = 0.95) , pars = c('ba','bb','be','bf','br'), labels = c('Akkermansia', 'Bacteroides','Enterococcus','Faecalibacterium','Ruminococcus'))  
# indicative of the Bacteroides link with toxicity  
```

```{r}
# make this plot myself with a pre-defined range in the axis
df <- precis(gtox,  prob = 0.95)  %>% as.tibble()
df <- df %>%
  mutate(variable = c('Akkermansia', 'Bacteroides','Enterococcus','Faecalibacterium','Ruminococcus'))

#remove row number 1 (The intercept)
df %>% 
  ggplot(aes(x = variable, y = mean)) +
  geom_point(shape = 15,
             size  = 4, width = 0.1,
             position = "dodge", color="black") +
  geom_errorbar(aes(ymin  = `2.5%`,
                    ymax  = `97.5%`),
                width = 0.1,
                size  = 0.7,
                position = "dodge", color="turquoise4") +
  theme(axis.title = element_text(face = "bold")) +
  xlab("Variables") + ylab("Coefficient with 95% CI") +
  coord_flip(ylim = c(-1.5, 1.5)) +
  geom_hline(yintercept = 0, color = "red", size = 1) +
   theme(axis.title = element_text(size = 0)) +
  theme(axis.text = element_text(size = 14)) +
  labs(title = 'Toxicity') +
  ggsave('../figs/amplicon/bayesian_genera_tox.pdf', width = 5, height = 4)
```

@@

```{r}
# make this plot myself with a pre-defined range in the axis
df <- precis(gcr,  prob = 0.95)  %>% as.tibble()
df <- df %>%
  mutate(variable = c('Akkermansia', 'Bacteroides','Enterococcus','Faecalibacterium','Ruminococcus'))

#remove row number 1 (The intercept)
df %>% 
  ggplot(aes(x = variable, y = mean)) +
  geom_point(shape = 15,
             size  = 4, width = 0.1,
             position = "dodge", color="black") +
  geom_errorbar(aes(ymin  = `2.5%`,
                    ymax  = `97.5%`),
                width = 0.1,
                size  = 0.7,
                position = "dodge", color="turquoise4") +
  theme(axis.title = element_text(face = "bold")) +
  xlab("Variables") + ylab("Coefficient with 95% CI") +
  coord_flip(ylim = c(-1.5, 1.5)) +
  geom_hline(yintercept = 0, color = "red", size = 1) +
   theme(axis.title = element_text(size = 0)) +
  theme(axis.text = element_text(size = 14)) +
  labs(title = 'CR') +
  ggsave('../figs/amplicon/bayesian_genera_cr.pdf', width = 5, height = 4)
```
